---
title:  'Computational Musicology'
author: 'Rolinde Zieverink'
date:   '2020'
output: 
    flexdashboard::flex_dashboard:
        storyboard: true
        theme: flatly
---

```{r setup}
# In order to use these packages, we need to install flexdashboard, plotly, and Cairo.
library(tidyverse)
library(plotly)
library(spotifyr)
source('spotify.R')
```

### Abstract
I want to know whether choirs who name themselves popchoirs are really popchoirs, that is, whether their repertoire mainly consists of songs in the genre pop. I will choose 10 different choirs and will analyse their repertoire. These can be found on their websites.

First, I chose the following 10 choirs:

Firma Vocaal, Weesp
Popolo, Nijmegen
Popkoor Koffer, Utrecht
Popkoor Prestige, Amsterdam
Popkoor Noisey Voices, Amsterdam
Popkoor Remix, Almere
Popkoor Amazing, Nieuwegein
Studentenpopkoor Plica Vocalis – Pop, Nijmegen
Hartkoor, Utrecht
Popkoor Akkoord, Roosendaal
Eurokoor, Leiden
Second, I made playlists for all the above mentioned choirs.

Third, I will compare each of these playlists with a playlist I make on my own -> Popmusic in Holland from 1965-2020.

Before I can compare the playlists which each other I need a definition of what popmusic in Holland is.

What I need to do for now/this week; https://www.top40.nl/bijzondere-lijsten/top-100-jaaroverzichten/1965 This website lists the 100 most popular songs in Holland of each year since 1965. Since 55 years with 100 songs is rather a lot of work I will focus on the first 40 songs of each year. This will be a total amount of songs of 2200. From here I can make the make the definition of what we could call in Holland popular music. After that I can start comparing all the popchoir playlists with the playlist I made for 'defining pop'


***

This is a second column of introductory text.


### Defining Pop Music

```{r}
grammy <- get_playlist_audio_features('digster.fm', '4kQovkgBZTd8h2HCM3fF31')
edison <- get_playlist_audio_features('spotify', '37i9dQZF1DX8mnKbIkppDf')
awards <-
    grammy %>% mutate(playlist = "Grammys") %>%
    bind_rows(edison %>% mutate(playlist = "Edisons"))
angry <-
    awards %>%                   # Start with awards.
    mutate(                      # Make pretty labels for mode.
        mode =                  
            factor(
                mode, 
                c(1, 0), 
                c("Major", "Minor")
            )
    ) %>% 
    ggplot(                      # Set up the plot.
        aes(
            x = valence,
            y = energy,
            size = loudness,
            colour = mode,
            label = track.name   # Labels will be interactively visible.
        )
    ) +
    geom_point() +               # Scatter plot.
    geom_rug(size = 0.1) +       # Add 'fringes' to show data distribution.
    facet_wrap(~ playlist) +     # Separate charts per playlist.
    scale_x_continuous(          # Fine-tune the x axis.
        limits = c(0, 1),
        breaks = c(0, 0.50, 1),  # Use grid-lines for quadrants only.
        minor_breaks = NULL      # Remove 'minor' grid-lines.
    ) +
    scale_y_continuous(          # Fine-tune the y axis in the same way.
        limits = c(0, 1),
        breaks = c(0, 0.50, 1),
        minor_breaks = NULL
    ) +
    scale_colour_brewer(         # Use the Color Brewer to choose a palette.
        type = "qual",           # Qualitative set.
        palette = "Paired"       # Name of the palette is 'Paired'.
    ) +
    scale_size_continuous(       # Fine-tune the sizes of each point.
        trans = "exp",           # Use an exp transformation to emphasise loud.
        guide = "none"           # Remove the legend for size.
    ) +
    theme_light() +              # Use a simpler them.
    labs(                        # Make the titles nice.
        x = "Valence",
        y = "Energy",
        colour = "Mode"
    )

ggplotly(angry)
```

***

For this visualisation from Week 7, I took playlists of the pop music presented at the Grammy awards (US) and the Edison awards (NL) in 2019. Using `ggplotly`, the visualisation became interactive.

The *x* axis shows valence and the *y* axis shows Spotify's ‘energy’ feature, which is roughly analogous to the notion of arousal in psychological research on emotion. Under this model, the quadrants of each graph, starting clockwise from the top left, represent angry, happy, relaxed, and sad music. The size of each point is proportional to the average volume of the track.

The visualisation shows that in 2019, the pop music at the Grammys was (according to Spotify) rather angrier and rather louder than the music at the Edisons.

remotes::install_github('jaburgoyne/compus')

### Popchoirs through



